What the hell is the title of this paper?

### 2018-05-13 NIPS 2018/main.tex
Updated up to TD

From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t. $\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t. $\bm{w}$. Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator. This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}). However, our transfer settings are rather different than common RL. In fact, our algorithm is likely to always start from $Q$-functions that are very close to the optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved. Unfortunately, this property cannot be guaranteed for most semi-gradient algorithms. Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching the optimum, and require a lot of tuning and tricks to work well. This is obviously an undesirable property in our case, as we only aim at adapting already good solutions. Thus, we consider using a residual gradient algorithm (after \cite{}\todo{Baird}). In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
\begin{equation}
\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
\end{equation}
where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions. The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}. Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t. the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$. Although residual algorithms have the sought guaranteed convergence, they are typically much slower than their semi-gradient counterpart. This problem was addressed in \cite{}\todo{Baird again}, where the authors proposed a simple remedy consisting in projecting the gradient in a direction that sill guarantees convergence but is also closer to the one of the semi-gradient, thus achieving higher learning speed. This can be easily done by including a parameter $\psi\in[0,1]$ in the TD error gradient such that:
\begin{equation}
\nabla_{\bm{w}}\norm{\wt{B}(\bm{w})}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right)
\end{equation}
where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$. Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$). A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee converge). Since in our case we are likely to start from this latter point, we consider only higher values (e.g., above $0.5$).

>>>>

From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t. $\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t. $\bm{w}$. Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator. This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}). However, our transfer settings are rather different than common RL. In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved. Unfortunately, this property cannot be guaranteed for most semi-gradient algorithms. Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching an optimum, and require many tricks and tuning to work well \cite{schaul2015prioritized,van2016deep}. This is obviously an undesirable property in our case, as we only aim at adapting already good solutions. Thus, we consider using a residual gradient algorithm \cite{baird1995residual}. In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
\begin{equation}
\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
\end{equation}
where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions. The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}. Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t. the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$. Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart. \cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence. This can be easily done by including a parameter $\psi\in[0,1]$ in the TD error gradient such that:
\begin{equation}
\nabla_{\bm{w}}\norm{\wt{B}(\bm{w})}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right)
\end{equation}
where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$. Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$). A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee converge).
